Hybrid Threads for the Parrot Virtual Machine

### 2012-02-25 Paper.tex
Describe schedule_proxied

As described in chapter~\ref{cha:design} to write to shared data, a thread creates a small task and schedules it on the data owning interpreter. Such a task could look like:
%
\begin{GenericCode}
.sub write_to_variable
    .param pmc variable
    variable = 1
.end
\end{GenericCode}
%
This is a subroutine with just one parameter. The variable passed in as this parameter is the one the task should write to. In this case the constant value 1 would be written to the variable. In PIR an assignment to a PMC gets translated as a method call. In this case the \textit{set\_integer\_native} would be called changing the variable's value. Since PMCs get passed by reference, it's the original variable which gets written to.

@@

>>>>

As described in chapter~\ref{cha:design} to write to shared data, a thread creates a small task and schedules it on the data owning interpreter. An example task could look like this:
%
\begin{GenericCode}
.sub write_to_variable
    .param pmc variable
    variable = 1
.end
\end{GenericCode}
%
This is a subroutine with just one parameter. The variable passed in as this parameter is the one the task should write to. In this case the constant value 1 would be written to the variable. In PIR an assignment to a PMC gets translated as a method call. In this case the \textit{set\_integer\_native} would be called changing the variable's value. Since PMCs get passed by reference, it's the original variable which gets written to.

@@

\textit{schedule\_proxied} uses \textit{Parrot\_thread\_create\_local\_task} which in this case detects that the \textit{data} given as parameter for the task's \textit{code} is actually a proxy already and unwraps the proxied object. \textit{Parrot\_cx\_schedule\_immediate} is then used to make the data owning interpreter execute the task as soon as possible.
